SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-10 docs/questioning.tex
from detection locus to point of detection

  By comparing the existing defenses and identifying their common
  characteristics, we help: a) researchers and practitioners to choose
  or modify a mechanism according to their needs, and b) designers of
  new approaches in developing more efficient mechanisms.
% @dimitro: change the above accordingly.

%In this paper we examine how application attack defense
%mechanism are developed and presented to
%the research community.
\end{abstract}

@@

%Introduction~\cite{I05}. Also see~\cite{A00}.

@@

In this paper we initially show how the above attacks can be seen from
a {\it common perspective}. We achieve this by providing an
exploitation model that highlights the following fact: the majority of
the steps needed to perform application attacks based on
source code injection are common.\footnote{Note that we leave out
  attacks that are based on binary code injection (i.e. buffer
  overflows --- see Section~\ref{sec:attacks}).} This is validated by
the fact that there are protection mechanisms that can detect more
than one of these attacks. Then, we {\it categorize} a selection of
these protection mechanisms. The selection comprises protection
mechanisms that detect such attacks and are presented in publications
cited more than twenty times, and some of the latest mechanisms that
have been presented in top security conferences that have been cited
less than twenty times. We included the second group so that we would
not penalize recent research. Finally, we {\it analyze} each mechanism based
on the following dimensions:
\begin{itemize}
\item {\it Accuracy} Protection mechanisms are as good
  as their detection capability; this requires low false positive and
  false negative rates.
\item {\it Computational Performance} We examine
  the overhead of the mechanisms
  that affect the experience of a web user who actually
  uses the protected application.
\item {\it Ease of use} We examine if the protection
  mechanism is practical in terms of deployment
  and can be easily adopted by security experts.
\item {\it Security} We examine how resilient is the system to
  attackers that know how it works and wants to circumvent it.
\item {\it Detection Locus} Based on our exploitation model
  we examine the location where a mechanism detects an attack.
\item {\it Availability} We check if the mechanism and its
  testbed are available on-line.
available 
\end{itemize}

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references:
locus {\sc x}~\cite{KJKV09,TNH07,NSS06,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
locus {\sc y}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
locus $\Omega$~\cite{BK04,LLW02,VMV05}.}
\end{figure*}

@@

The first two criteria are \emph{Accuracy} and
\emph{Availability}. The other four criteria are \emph{Computational
  Performance}, \emph{Ease of Use}, \emph{Security}, and
\emph{Detection Locus}.

@@

\subsection{Detection Locus}

Detection mechanisms vary on the location where they detect an attack.
There are five different loci where an attack can be caught, as seen
in Figure~\ref{fig:attacks}:
\begin{itemize}
\item At the user's browser (Locus X).
\item En route from the server to the user's browser (Locus Y).
\item Embedded in a query, but before it reaches the server's database
  (Locus Z).
\item After the malicious code has been executed on the server's
  database (Locus $\Omega$).
\end{itemize}

@@

In the case of {\sc dsl} injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Both mechanisms that implement this approach,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06} are pretty similar
and detect the attack before a query reaches the
database (Locus {\sc z}).
Contrary to {\sc sqlg}uard (and other
mechanisms as we will observe), {\sc sql}check has been
extensively tested in terms of accuracy
as it can be seen in Table~\ref{tab:comp}.
A disadvantage of those mechanisms is that the
application must be modified in every code fragment
that sends an {\sc sql} query to the database for execution.

@@

{\it Noxes}~\cite{KKVJ06,KJKV09} is the only
framework that partially allows the web
user to specify policies to prevent {\sc xss} attacks.
The key idea behind Noxes is to parse
the {\sc html} that reaches the browser to
find static {\sc url} references. Then, based on
a set of policies Noxes allows or blocks
the request (Locus {\sc x}). Such policies
can be also provided by the server (i.e. ``never
follow a link that leads to the malicious.com
web site"). The main issue with Noxes is that
it does not deal with JavaScript-driven {\sc xss}
attacks which is currently the most popular
{\sc xss} attack vector.

A number of the frameworks define policies
based on information and features provided by
the Document Object Model ({\sc dom}) of a web page.
Specifically, developers must place all legitimate
scripts inside {\sc html} elements like {\tt div}.
The web browser (Locus {\sc x}), parses the
{\sc dom} tree and executes scripts only when they
are contained in such elements. All other scripts
are treated according to the policies defined
on the server. Frameworks that support this
functionality are {\sc beep}~\cite{TNH07}
and {\sc dsi}~\cite{NSS06}. The main problem with
the above mechanisms is that they are vulnerable
to non-persistent {\sc xss} attacks that alter
the {\sc dom} of an already rendered
page~\cite{APKLM10}.
In addition, a recent variation of JavaScript
injection attacks known as return-to-JavaScript
attack can be used to bypass the above mechanisms
as described extensively in reference~\cite{APKLM10}.
% Such attacks share
% many similarities with the {\it return-to-lib}
% attack~\cite{SPPGMMB04}. 
%% PL Explain what it does, I guess it's what you go on to say
%% directly below?
% When performing an attack like this the malicious user transfers the
% execution to points that contain script code which in turn is used to
% perform the attack.

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
acts as a proxy on the server side (Locus {\sc y}) to
parse the {\sc html} of server responses and identifies
scripts. Then, it rewrites them into safe equivalents
and protects the web user from exploits
that are based on reported browser vulnerabilities.
{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
and the framework by {\it Phung et al.}~\cite{PSC09}
extend JavaScript with new primitive functions that
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place on the JavaScript engine of the browser (Locus {\sc x}).
%% PL In which way is this a kind of policy enforcement?
In this way, {\sc xxs} attacks that take advantage
functions like {\tt write} and {\tt eval}, which are
used to assemble innocuous-looking parts into harmful
strings,\footnote{The infamous Sammy worm that
infected MySpace in 2005~\cite{SP07,ELX07}
utilized the {\tt eval} function to assemble a
script with malicious behavior.} would fail.

@@

\noindent
{\it WebJail}~\cite{VDDPJ11}, and
{\sc soma}~\cite{OWVS08} are two frameworks that
can actually detect such an attack (Locus {\sc x}).
To achieve this, {\sc soma} requires site administrators
to specify legitimate, external domains for sending
or receiving information in order to approve interactions
between them and the protected web site. As a result,
{\sc soma} can also detect {\sc csrf} attacks.
WebJail contains the functionality of third-party scripts
by introducing a web component integrator that restricts
the access that these scripts may have to either the data
or the functionality of other components.

Policy enforcement mechanisms that detect {\sc csrf}
attacks are usually implemented in the form of a
server-side proxy (Locus {\sc y})
interposing on the client-server communication, and modifying
it. {\it NoForge}~\cite{JKK06a}
parses the {\sc html} server responses
and adds a token to every {\sc url} referring to this
server. Then it associates the token with the cookie
representing the session {\sc id} for the application.
When a request is received, the mechanism checks
if the request contains the token related
to the session {\sc id}. A disadvantage of NoForge
is that {\sc html} that is dynamically created within
the browser will not include the token.
Thus, sites that create their {\sc html} on the client
will remain vulnerable. In addition, it does not
support cross-origin requests.
{\it j{\sc csrf}}~\cite{PS11}
has a very similar functionality and meanwhile
addresses the above problems.
Finally, {\it CsFire}~\cite{DDHPJ10}
examines cross-domain interactions, to design a
cross-domain policy on the client's side (Locus {\sc x}).
The policy is based on the concept of a relaxed
same-origin policy that allows communication between
sub-domains of the same registered domain.

@@

{\it {\sc sql}rand}~\cite{BK04} implements {\sc isr} to detect {\sc
  sql} injection attacks. It allows programmers to create {\sc sql}
statements using randomized instructions instead of standard keywords.
The modified queries are reconstructed at runtime using the same key
that is inaccessible to the malicious user. {\sc sql}rand is one of
the few mechanisms that detect {\sc sql} injection attacks on the
database level (Locus $\Omega$).

In the case of {\sc xss} attacks that are based on JavaScript or {\sc
  html}, consider a {\sc xor} function that encodes all source of a
web page on the server-side and then, on the client-side, the web
browser decodes the source by applying the same function again (Locus
{\sc x}). Variations of this approach include {\it
  Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}, which
randomize the instruction set of {\sc html} and JavaScript
respectively. Contrary to x{\sc js}, in Noncespaces administrators
must set specific policies in a manner similar to a firewall
configuration language. This fact, together with the insufficient
testing of the mechanism (see Table~\ref{tab:comp}) brings up
questions concerning its accuracy. {\it {\sc
    sm}ask}~\cite{JB07} is another framework that was inspired by {\sc
  isr}. To detect {\sc xss} attacks it searches for {\sc html} and
JavaScript keywords within the application's legitimate code. This is
done before the processing of an {\sc http} request. When it finds one
it adds a token to it. This results to a ``code mask". Then, before
sending the resulting {\sc html} data to the web user, the framework
searches the data for illegal code by using the same keywords (Locus
{\sc y}). Since all legitimate code has been ``masked", the injected
code can be identified. The pre- and post-processing of the code
though, may add a significant overhead to the application.
Unfortunately, the authors of {\sc sm}ask did not provide measurements
regarding the computational performance of the tool (see
Table~\ref{tab:comp}).

@@

There are different implementations of this approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (Locus {\sc z}).
% However, this is a simplistic approach that may
% lead to many false positives.
%% PL better to avoid characterisations and mention only the facts
%% (that it leads to many false positives, as shown by ...

It is possible to apply further checks when it is established that
tainted data have reached a sink (Locus {\sc z}). {\it Xu et
  al.}~\cite{XBS06} track taint information at the level of bytes in
memory. To distinguish between legitimate and malicious uses of
untrusted data that reach a sink, they search the data for suspicious
symbols by using regular expressions. {\sc csse}~\cite{PB05}
associates tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application,
and others. When tainted data reaches a sink, {\sc csse} performs
syntactic checks based on the aforementioned metadata (Locus {\sc z}).
{\it {\sc php} Aspis}~\cite{PMP11} works in a similar way. To obtain
metadata, it takes advantage of {\sc php} arrays data structure.
%% PL Like what?
% Note that the above schemes detect potential attacks
% in locus {\sc z}. This automatically means that they
% cannot detect non-persistent JavaScript-driven
% {\sc xss} attacks. Although they can be
% modified to do so.
Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
if there are tainted data that contain scripts (locus {\sc y}).

@@

{\it Vogt et al.}~\cite{VFJKKV07} have developed a tainting scheme
that follows a different approach. Contrary to the aforementioned
schemes that operate on the server side, they track sensitive
information on the client side (Locus {\sc x}). This is a form of
positive taint tracking, where taint data is considered to be
legitimate. Their scheme detects JavaScript-driven {\sc xss} attacks
by ensuring that a script can send sensitive user data only to the
site from which it came from.
% This though, may lead to false alarms.
%% PL You mean a lot of false alarms?
{\it Stock et al.}~\cite{SLMS14} propose a scheme that also operates
in the browser (Locus {\sc x}). The scheme focuses on the detection of
{\sc dom}-based {\sc xss} attacks. In such an attack, the malicious
payload is executed as a result of the modification of the {\sc dom}
environment so that the client-side code runs in an unanticipated
manner even if the {\sc http} response that triggers the injection
seems legitimate. The scheme is different from the previous one
because it marks and observes data that are considered harmful.
Specifically, it employs a taint-enhanced JavaScript engine that
tracks the flow of attacker-controlled data. To detect potential
attacks the scheme utilizes {\sc html} and JavaScript parsers that can
identify the generation of code coming from tainted data.

@@

Training methods that detect {\sc dsl}-driven injection attacks
generate and store valid code statements (i.e. {\sc sql} or {\sc
  xp}ath queries) in various forms, and detect attacks as outliers
from the set of valid code statements. An early approach, {\it {\sc
    didafit}}~\cite{LLW02} detects {\sc sql} injection (Locus
$\Omega$) attacks by recording all database transactions
(stripped from user input). Subsequent
refinements by Valeur et al.~\cite{VMV05} tagged each transaction with
the corresponding application as an extension of their anomaly
detection framework called {\it libAnomaly}. {\it {\sc
    sd}river}~\cite{MS09,MKS09,MKLS11} is a signature-based mechanism
that prevents {\sc sql} and {\sc xp}ath injection attacks. The
signatures generated during a training phase are based on features
that can depend either on the code statement or on its execution
environment (i.e. the stack trace). Then, at runtime, the mechanism
checks all statements for compliance and can block code statements
containing injected elements (Locus {\sc z}). {\sc
  amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects {\sc
  sql} injection attacks (locus {\sc z}) by associating a query model
with the location of every {\sc sql} statement within the application.
Then, at runtime, it monitors the application's execution to detect
when {\sc sql} statements diverge from the expected model.

Various countermeasures against {\sc xss} attacks follow a similar
pattern. {\it {\sc swap}}~\cite{WPLKK09} creates a unique identifier
({\it script {\sc id}}) for every legitimate script on the server.
Then, a JavaScript detection component placed in a web proxy (Locus
{\sc y}) searches for injected scripts with no corresponding {\sc id}
in the server's responses. If no injected scripts are found, the proxy
forwards the request to the client. This mechanism is relatively
inflexible since it does not support dynamic scripts. In addition it
imposes a significant overhead (see Table~\ref{tab:comp}). The authors
of {\it {\sc xssds}}~\cite{JEP08} have implemented a similar mechanism
that also supports dynamic and external scripts. Specifically, during
training phase they build a list of all benign scripts. In the case of
external scripts they keep a white list of all the valid domain names
that contain scripts used by the application.

@@

{\sc xss-guard}~\cite{BV08} is a training scheme that also employs
parse-tree validation. During training, the scheme maps legitimate
scripts to {\sc http} responses. During production {\sc xss-guard}
retrieves for every script included in a response its parsed tree and
checks if it is one of those previously mapped to this response. Apart
from the comparison of the parsed trees, {\sc xss-guard} checks also
for an exact match of lexical entities. To achieve this, the scheme
utilizes that data structures of Firefox's JavaScript engine (Locus
{\sc x}). However, string literals are not compared literally and
therefore a false negative result could occur if an adversary performs
a mimicry attack~\cite{WS02}. For example, consider a banner rotator
that every time it runs, it creates a value that depends on the
current date and the length of the array that contains the references
of the various images to be displayed. Then, based on this value it
shows a specific image to a user. In a vulnerable web site that allows
users to post data and contains this banner rotator, a malicious user
could create and store a script that has the same code structure, with
the same JavaScript keywords contained in the rotator script.
%% PL You mean like the rotator?
In this script the attacker could also include references to tiny
images hosted on a web server that is maintained by him in order to
retrieve the {\sc ip} addresses of the users that visit the vulnerable
site.

{\it Blueprint}~\cite{LV09} is a policy enforcement framework that
also utilizes parsed trees to detect {\sc xss} attacks. To guarantee
that untrusted content is not executed, Blueprint generates on the
server-side a parsed tree from untrusted {\sc html} to ensure that it
does not contain any dynamic content. Then the parsed tree is
transfered to the document generator of the browser (Locus {\sc x})
where untrusted browser parsing behavior is ruled out. Blueprint is an
efficient countermeasure but it imposes a significant overhead due to
its extensive parsing (see Table~\ref{tab:comp}).

{\it Diglossia}~\cite{SMS13} combines positive taint tracking (see
Subsubsection~\ref{sec:taint}) together with parse-tree validation.
Diglossia was based on the theory of Ray and Ligatti~\cite{RL12b}
(also see Section~\ref{sec:attacks}) to detect {\sc dsl} code
injection attacks. In addition, it is actually the first, and so far
the only framework that detects No{\sc sql} injection attacks. When an
application computes an output string (query), Diglossia computes a
``shadow" of this string. Specifically, it maps all characters
introduced by the application to a shadow character set. This set does
not contain any characters coming from the tainted input. Then, the
scheme creates the tree of the query that is about to be executed and
compares it with the parsed tree of the ``shadow" (Locus {\sc z}). If
the trees are not equal the application is probably under attack. Note
that Diglossia can be bypassed in the same way as other taint
tracking approaches as described in reference~\cite{NBR14}.
%% PL which way is this exactly?

@@

\subsection{Detection Locus}

>>>>

  By comparing the existing defenses and identifying their common
  characteristics, we help: a) researchers and practitioners to choose
  or modify a mechanism according to their needs, and b) designers of
  new approaches in developing more efficient mechanisms.
% dimitro@dimitro: change the above accordingly.

\end{abstract}

@@

@@

In this paper we initially show how the above attacks can be seen from
a {\it common perspective}. We achieve this by providing an
exploitation model that highlights the following fact: the majority of
the steps needed to perform application attacks based on
source code injection are common.\footnote{Note that we leave out
  attacks that are based on binary code injection (i.e. buffer
  overflows --- see Section~\ref{sec:attacks}).} This is validated by
the fact that there are protection mechanisms that can detect more
than one of these attacks. Then, we {\it categorize} a selection of
these protection mechanisms. The selection comprises protection
mechanisms that detect such attacks and are presented in publications
cited more than twenty times, and some of the latest mechanisms that
have been presented in top security conferences that have been cited
less than twenty times. We included the second group so that we would
not penalize recent research. Finally, we {\it analyze} each mechanism based
on the following dimensions:
\begin{itemize}
\item {\it Accuracy} Protection mechanisms are as good
  as their detection capability; this requires low false positive and
  false negative rates.
\item {\it Computational Performance} We examine
  the overhead of the mechanisms
  that affect the experience of a web user who actually
  uses the protected application.
\item {\it Ease of use} We examine if the protection
  mechanism is practical in terms of deployment
  and can be easily adopted by security experts.
\item {\it Security} We examine how resilient is the system to
  attackers that know how it works and wants to circumvent it.
\item {\it Point of Detection} Based on our exploitation model
  we examine the location where a mechanism detects an attack.
\item {\it Availability} We check if the mechanism and its
  testbed are available on-line.
available 
\end{itemize}

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it point} indicates a step where mechanisms
detect attacks. For every point we provide the corresponding
references:
Point {\sc ub}~\cite{KJKV09,TNH07,NSS06,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
Point {\sc sb}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
Point {\sc eq}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
Point {\sc sdb}~\cite{BK04,LLW02,VMV05}.}
\end{figure*}

@@

The first two criteria are \emph{Accuracy} and
\emph{Availability}. The other four criteria are \emph{Computational
  Performance}, \emph{Ease of Use}, \emph{Security}, and
\emph{Point of Detection}.

@@

\subsection{Point of Detection}

Detection mechanisms vary on the location where they detect an attack.
There are four different points where an attack can be caught, as seen
in Figure~\ref{fig:attacks}:
\begin{itemize}
\item At the user's browser (Point {\sc ub}).
\item En route from the server to the user's browser --- in most cases
within a proxy (Point {\sc sb}).
\item Embedded in a query, but before it reaches the server's database
  (Point {\sc eq}).
\item After the malicious code has been executed on the server's
  database (Point {\sc sdb}).
\end{itemize}

@@

In the case of {\sc dsl} injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Both mechanisms that implement this approach,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06} are pretty similar
and detect the attack before a query reaches the
database (Point {\sc eq}).
Contrary to {\sc sqlg}uard (and other
mechanisms as we will observe), {\sc sql}check has been
extensively tested in terms of accuracy
as it can be seen in Table~\ref{tab:comp}.
A disadvantage of those mechanisms is that the
application must be modified in every code fragment
that sends an {\sc sql} query to the database for execution.

@@

{\it Noxes}~\cite{KKVJ06,KJKV09} is the only
framework that partially allows the web
user to specify policies to prevent {\sc xss} attacks.
The key idea behind Noxes is to parse
the {\sc html} that reaches the browser to
find static {\sc url} references. Then, based on
a set of policies Noxes allows or blocks
the request (Point {\sc ub}). Such policies
can be also provided by the server (i.e. ``never
follow a link that leads to the malicious.com
web site"). The main issue with Noxes is that
it does not deal with JavaScript-driven {\sc xss}
attacks which is currently the most popular
{\sc xss} attack vector.

A number of the frameworks define policies
based on information and features provided by
the Document Object Model ({\sc dom}) of a web page.
Specifically, developers must place all legitimate
scripts inside {\sc html} elements like {\tt div}.
The web browser (Point {\sc ub}), parses the
{\sc dom} tree and executes scripts only when they
are contained in such elements. All other scripts
are treated according to the policies defined
on the server. Frameworks that support this
functionality are {\sc beep}~\cite{TNH07}
and {\sc dsi}~\cite{NSS06}. The main problem with
the above mechanisms is that they are vulnerable
to non-persistent {\sc xss} attacks that alter
the {\sc dom} of an already rendered
page~\cite{APKLM10}.
In addition, a recent variation of JavaScript
injection attacks known as return-to-JavaScript
attack can be used to bypass the above mechanisms
as described extensively in reference~\cite{APKLM10}.
% Such attacks share
% many similarities with the {\it return-to-lib}
% attack~\cite{SPPGMMB04}. 
%% PL Explain what it does, I guess it's what you go on to say
%% directly below?
% When performing an attack like this the malicious user transfers the
% execution to points that contain script code which in turn is used to
% perform the attack.

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
acts as a proxy on the server side (Point {\sc SB}) to
parse the {\sc html} of server responses and identifies
scripts. Then, it rewrites them into safe equivalents
and protects the web user from exploits
that are based on reported browser vulnerabilities.
{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
and the framework by {\it Phung et al.}~\cite{PSC09}
extend JavaScript with new primitive functions that
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place on the JavaScript engine of the browser (Point {\sc ub}).
%% PL In which way is this a kind of policy enforcement?
In this way, {\sc xxs} attacks that take advantage
functions like {\tt write} and {\tt eval}, which are
used to assemble innocuous-looking parts into harmful
strings,\footnote{The infamous Sammy worm that
infected MySpace in 2005~\cite{SP07,ELX07}
utilized the {\tt eval} function to assemble a
script with malicious behavior.} would fail.

@@

\noindent
{\it WebJail}~\cite{VDDPJ11}, and
{\sc soma}~\cite{OWVS08} are two frameworks that
can actually detect such an attack (Point {\sc ub}).
To achieve this, {\sc soma} requires site administrators
to specify legitimate, external domains for sending
or receiving information in order to approve interactions
between them and the protected web site. As a result,
{\sc soma} can also detect {\sc csrf} attacks.
WebJail contains the functionality of third-party scripts
by introducing a web component integrator that restricts
the access that these scripts may have to either the data
or the functionality of other components.

Policy enforcement mechanisms that detect {\sc csrf}
attacks are usually implemented in the form of a
server-side proxy (Point {\sc SB})
interposing on the client-server communication, and modifying
it. {\it NoForge}~\cite{JKK06a}
parses the {\sc html} server responses
and adds a token to every {\sc url} referring to this
server. Then it associates the token with the cookie
representing the session {\sc id} for the application.
When a request is received, the mechanism checks
if the request contains the token related
to the session {\sc id}. A disadvantage of NoForge
is that {\sc html} that is dynamically created within
the browser will not include the token.
Thus, sites that create their {\sc html} on the client
will remain vulnerable. In addition, it does not
support cross-origin requests.
{\it j{\sc csrf}}~\cite{PS11}
has a very similar functionality and meanwhile
addresses the above problems.
Finally, {\it CsFire}~\cite{DDHPJ10}
examines cross-domain interactions, to design a
cross-domain policy on the client's side (Point {\sc ub}).
The policy is based on the concept of a relaxed
same-origin policy that allows communication between
sub-domains of the same registered domain.

@@

{\it {\sc sql}rand}~\cite{BK04} implements {\sc isr} to detect {\sc
  sql} injection attacks. It allows programmers to create {\sc sql}
statements using randomized instructions instead of standard keywords.
The modified queries are reconstructed at runtime using the same key
that is inaccessible to the malicious user. {\sc sql}rand is one of
the few mechanisms that detect {\sc sql} injection attacks on the
database level (Point {\sc sdb}).

In the case of {\sc xss} attacks that are based on JavaScript or {\sc
  html}, consider a {\sc xor} function that encodes all source of a
web page on the server-side and then, on the client-side, the web
browser decodes the source by applying the same function again (Point
{\sc ub}). Variations of this approach include {\it
  Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}, which
randomize the instruction set of {\sc html} and JavaScript
respectively. Contrary to x{\sc js}, in Noncespaces administrators
must set specific policies in a manner similar to a firewall
configuration language. This fact, together with the insufficient
testing of the mechanism (see Table~\ref{tab:comp}) brings up
questions concerning its accuracy. {\it {\sc
    sm}ask}~\cite{JB07} is another framework that was inspired by {\sc
  isr}. To detect {\sc xss} attacks it searches for {\sc html} and
JavaScript keywords within the application's legitimate code. This is
done before the processing of an {\sc http} request. When it finds one
it adds a token to it. This results to a ``code mask". Then, before
sending the resulting {\sc html} data to the web user, the framework
searches the data for illegal code by using the same keywords (Point
{\sc SB}). Since all legitimate code has been ``masked", the injected
code can be identified. The pre- and post-processing of the code
though, may add a significant overhead to the application.
Unfortunately, the authors of {\sc sm}ask did not provide measurements
regarding the computational performance of the tool (see
Table~\ref{tab:comp}).

@@

There are different implementations of this approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (Point {\sc eq}).
% However, this is a simplistic approach that may
% lead to many false positives.
%% PL better to avoid characterisations and mention only the facts
%% (that it leads to many false positives, as shown by ...

It is possible to apply further checks when it is established that
tainted data have reached a sink (Point {\sc eq}). {\it Xu et
  al.}~\cite{XBS06} track taint information at the level of bytes in
memory. To distinguish between legitimate and malicious uses of
untrusted data that reach a sink, they search the data for suspicious
symbols by using regular expressions. {\sc csse}~\cite{PB05}
associates tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application,
and others. When tainted data reaches a sink, {\sc csse} performs
syntactic checks based on the aforementioned metadata (Point {\sc eq}).
{\it {\sc php} Aspis}~\cite{PMP11} works in a similar way. To obtain
metadata, it takes advantage of {\sc php} arrays data structure.
%% PL Like what?
% Note that the above schemes detect potential attacks
% in locus {\sc z}. This automatically means that they
% cannot detect non-persistent JavaScript-driven
% {\sc xss} attacks. Although they can be
% modified to do so.
Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
if there are tainted data that contain scripts (Point {\sc sb}).

@@

{\it Vogt et al.}~\cite{VFJKKV07} have developed a tainting scheme
that follows a different approach. Contrary to the aforementioned
schemes that operate on the server side, they track sensitive
information on the client side (Point {\sc ub}). This is a form of
positive taint tracking, where taint data is considered to be
legitimate. Their scheme detects JavaScript-driven {\sc xss} attacks
by ensuring that a script can send sensitive user data only to the
site from which it came from.
% This though, may lead to false alarms.
%% PL You mean a lot of false alarms?
{\it Stock et al.}~\cite{SLMS14} propose a scheme that also operates
in the browser (Point {\sc ub}). The scheme focuses on the detection of
{\sc dom}-based {\sc xss} attacks. In such an attack, the malicious
payload is executed as a result of the modification of the {\sc dom}
environment so that the client-side code runs in an unanticipated
manner even if the {\sc http} response that triggers the injection
seems legitimate. The scheme is different from the previous one
because it marks and observes data that are considered harmful.
Specifically, it employs a taint-enhanced JavaScript engine that
tracks the flow of attacker-controlled data. To detect potential
attacks the scheme utilizes {\sc html} and JavaScript parsers that can
identify the generation of code coming from tainted data.

@@

Training methods that detect {\sc dsl}-driven injection attacks
generate and store valid code statements (i.e. {\sc sql} or {\sc
  xp}ath queries) in various forms, and detect attacks as outliers
from the set of valid code statements. An early approach, {\it {\sc
    didafit}}~\cite{LLW02} detects {\sc sql} injection (Point
sdb) attacks by recording all database transactions
(stripped from user input). Subsequent
refinements by Valeur et al.~\cite{VMV05} tagged each transaction with
the corresponding application as an extension of their anomaly
detection framework called {\it libAnomaly}. {\it {\sc
    sd}river}~\cite{MS09,MKS09,MKLS11} is a signature-based mechanism
that prevents {\sc sql} and {\sc xp}ath injection attacks. The
signatures generated during a training phase are based on features
that can depend either on the code statement or on its execution
environment (i.e. the stack trace). Then, at runtime, the mechanism
checks all statements for compliance and can block code statements
containing injected elements (Point {\sc eq}). {\sc
  amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects {\sc
  sql} injection attacks (Point {\sc eq}) by associating a query model
with the location of every {\sc sql} statement within the application.
Then, at runtime, it monitors the application's execution to detect
when {\sc sql} statements diverge from the expected model.

Various countermeasures against {\sc xss} attacks follow a similar
pattern. {\it {\sc swap}}~\cite{WPLKK09} creates a unique identifier
({\it script {\sc id}}) for every legitimate script on the server.
Then, a JavaScript detection component placed in a web proxy (Point
{\sc sb}) searches for injected scripts with no corresponding {\sc id}
in the server's responses. If no injected scripts are found, the proxy
forwards the request to the client. This mechanism is relatively
inflexible since it does not support dynamic scripts. In addition it
imposes a significant overhead (see Table~\ref{tab:comp}). The authors
of {\it {\sc xssds}}~\cite{JEP08} have implemented a similar mechanism
that also supports dynamic and external scripts. Specifically, during
training phase they build a list of all benign scripts. In the case of
external scripts they keep a white list of all the valid domain names
that contain scripts used by the application.

@@

{\sc xss-guard}~\cite{BV08} is a training scheme that also employs
parse-tree validation. During training, the scheme maps legitimate
scripts to {\sc http} responses. During production {\sc xss-guard}
retrieves for every script included in a response its parsed tree and
checks if it is one of those previously mapped to this response. Apart
from the comparison of the parsed trees, {\sc xss-guard} checks also
for an exact match of lexical entities. To achieve this, the scheme
utilizes that data structures of Firefox's JavaScript engine (Point
{\sc ub}). However, string literals are not compared literally and
therefore a false negative result could occur if an adversary performs
a mimicry attack~\cite{WS02}. For example, consider a banner rotator
that every time it runs, it creates a value that depends on the
current date and the length of the array that contains the references
of the various images to be displayed. Then, based on this value it
shows a specific image to a user. In a vulnerable web site that allows
users to post data and contains this banner rotator, a malicious user
could create and store a script that has the same code structure, with
the same JavaScript keywords contained in the rotator script.
%% PL You mean like the rotator?
In this script the attacker could also include references to tiny
images hosted on a web server that is maintained by him in order to
retrieve the {\sc ip} addresses of the users that visit the vulnerable
site.

{\it Blueprint}~\cite{LV09} is a policy enforcement framework that
also utilizes parsed trees to detect {\sc xss} attacks. To guarantee
that untrusted content is not executed, Blueprint generates on the
server-side a parsed tree from untrusted {\sc html} to ensure that it
does not contain any dynamic content. Then the parsed tree is
transfered to the document generator of the browser (Point {\sc ub})
where untrusted browser parsing behavior is ruled out. Blueprint is an
efficient countermeasure but it imposes a significant overhead due to
its extensive parsing (see Table~\ref{tab:comp}).

{\it Diglossia}~\cite{SMS13} combines positive taint tracking (see
Subsubsection~\ref{sec:taint}) together with parse-tree validation.
Diglossia was based on the theory of Ray and Ligatti~\cite{RL12b}
(also see Section~\ref{sec:attacks}) to detect {\sc dsl} code
injection attacks. In addition, it is actually the first, and so far
the only framework that detects No{\sc sql} injection attacks. When an
application computes an output string (query), Diglossia computes a
``shadow" of this string. Specifically, it maps all characters
introduced by the application to a shadow character set. This set does
not contain any characters coming from the tainted input. Then, the
scheme creates the tree of the query that is about to be executed and
compares it with the parsed tree of the ``shadow" (Point {\sc eq}). If
the trees are not equal the application is probably under attack. Note
that Diglossia can be bypassed in the same way as other taint
tracking approaches as described in reference~\cite{NBR14}.
%% PL which way is this exactly?

@@

\subsection{Point of Detection}

Given the fact that the final steps of
{\sc dsl} injection and {\sc csrf} attacks take place
on the server-side, all the mechanisms that detect
such attacks are placed in some point within the server.
From the mechanisms that detect {\sc dsl} code injection
attacks, 3 out of 13 (23\%) do so at the level
of the {\sc rdbms}---Point {\sc sdb}.
The other 11 wrap {\sc api} calls related to output
vectors---Point {\sc eq}.
